PANCHANGE_analysis

### 2020-09-02 PANCHANGE_analysis.Rmd
Small edits to the set-up and comment about summarising whole datset.

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
#install.packages("broom")
#install.packages("skimr")
```

@@

```{r source file path}
#source raw data directory: data.raw_path
source("../PANCHANGE_raw_path.R")
```

@@

```{r dat.coping summary, eval=FALSE, include=FALSE}
summarytools::dfSummary(
  dat.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

>>>>

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
#install.packages("broom")
#install.packages("skimr")
#install.packages("polycor")
#install.packages("corrplot")
#install.packages("patchwork")
```

@@

```{r source file path}
#source data directory: data_path
source("../PANCHANGE_raw_path.R")
```

@@

++MD: I had to cancel this chunk while running because it took too long - there are 473 variables in this dataset, so I don't think summarising all at once is useful!
```{r dat.coping summary, eval=FALSE, include=FALSE}
summarytools::dfSummary(
  dat.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```
